Nuclei Segmentation in Histopathology images using Deep Neural Networks

### 2017-01-18 Paper.tex
update of table
what changes

\begin{figure}[htb]
\begin{minipage}[b]{.48\linewidth}
  \centering
  \centerline{\includegraphics[width=4.0cm]{RGB_1}}
%  \vspace{1.5cm}
  \centerline{Sample from patient 498959}\medskip
\end{minipage}
\hfill
\begin{minipage}[b]{0.48\linewidth}
  \centering
  \centerline{\includegraphics[width=4.0cm]{GT_1}}
%  \vspace{1.5cm}
  \centerline{Associated ground truth}\medskip
\end{minipage}
%
%
%\begin{minipage}[b]{.48\linewidth}
 % \centering
%  \centerline{\includegraphics[width=4.0cm]{RGB_2}}
%  \vspace{1.5cm}
%  \centerline{Sample from patient 581910}\medskip
%\end{minipage}
%\hfill
%\begin{minipage}[b]{0.48\linewidth}
%  \centering
%  \centerline{\includegraphics[width=4.0cm]{GT_2}}
%  \vspace{1.5cm}
%  \centerline{Associated ground truth}\medskip
%\end{minipage}
%
%
\begin{minipage}[b]{.48\linewidth}
  \centering
  \centerline{\includegraphics[width=4.0cm]{RGB_3}}
%  \vspace{1.5cm}
  \centerline{Another one from patient 581910}\medskip
\end{minipage}
\hfill
\begin{minipage}[b]{0.48\linewidth}
  \centering
  \centerline{\includegraphics[width=4.0cm]{GT_3}}
%  \vspace{1.5cm}
  \centerline{Associated ground truth}\medskip
\end{minipage}
%
\caption{Random annotated samples from the dataset}
\label{fig:annotation}
%
\end{figure}

@@

%% Contribution as a dataset, small introduction
\noindent One of the contributions of this paper is the now publicly available 
nuclei detection dataset within HE stained histopathology images which 
can be found at \url{http://cbio.mines-paristech.fr/~pnaylor/BNS.zip} 
(not a true address). This annotated dataset provides images clustered by 
patients. Each patient has at least 3 annotated $512 \times 512$ HE 
histopathology images with their associated ground truth. Each 
ground truth image is a $512 \times 512$ label image where each pixel value above 
$0$ is considered as the label of the corresponding nucleus. 
See figure \ref{fig:annotation} for an example of 
three annotated images. This annotation was conducted via the help of 
the software ITK-snap, \cite{py06nimg} \url{http://www.itksnap.org} by
the authors of this paper.

@@

%% Validation scheme
We have our training set $(A_l,B_l)_{l \in [1, N]}$ where N is equal to 
33, however each element $A_l$ belongs to a certain patients and 
several elements $A_l$ can belong to the same patient. As we are 
dealing with histopathology images, it is known that samples can widely 
vary from one patient to the other. We thus validate our model by a 
leave one patient out scheme. 
For this reason we use a leave-one-patient-out strategy: for a 
given set of hyper parameters, we 
train our model on every patient except one that is used for validation. 
Our final score is averaged over all patients.
Several metrics give a detailed assessment of the model quality: accuracy, 
F1 score and a performance score which is the mean between 
true positive rate and true negative rate.

@@

\section{Results and discussion}
\label{sec:result}
\noindent We conducted our experiments on GPUs via the caffe framework, 
\cite{jia2014caffe}. We present our results in table \ref{tab:res} where 
we averaged the metrics over all left out patients. We also added, for 
illustration purposes \ref{fig:prediction}, image predictions and 
associated 
probability maps to evaluate some differences between the classifiers. 
We notice that the simpler net, PangNet seems to have learnt simple 
rules such as color information. As soon as the nuclei are not
homogeneous and dark inside, the method fails ( "holes" in the
cells). On the 
contrary, deeper nets as FCN and DeconvNet have learnt deeper features 
and seem capable of recognizing whole cells. On these probability maps 
we applied our watershed segmentation and we can picture the results in 
the third 
column. By construction, our post-processing 
scheme is very sensitive to noise as we can see in the PangNet 
prediction, many unrelated minimas will lead to highly partitionned cell. 
This phenomenom also appears with the DeconvNet where undesired 
cuts were performed, like for the cell at the bottom left of the image. 
We picked $\lambda = 7$ which seemed to give a nice partitionning of 
the image, this value can be found by cross validation or by simple 
visualization of the results.
\begin{table}
\begin{tabular}{|c|c|c|c|c|}
\hline
  & PangNet & DeconvNet & FCN & Ensemble\\
 \hline
Accuracy  &       0.936 & 0.968 &0.958 & 0.968  \\
IU   &    0.759 &     0.856 & 0.857 & 0.861 \\
Recall     &       0.744  &     0.856 & 0.855 & 0.876\\
Precision   &       0.741 &     0.858 & 0.878 & 0.851\\
F1    &       0.742 &     0.856 & 0.866  & 0.863\\
% TP       &       0.744 &     0.856 & 0.855 & 0.876 \\
% TN      &       0.963 &     0.981 &  0.977 & 0.979\\
Performance    &       0.853 &     0.918 & 0.916 & 0.928\\
% Pixel error  &  0.063 &     0.032 & 0.042 & 0.032\\
\hline
\end{tabular}
\caption{Results}
\label{tab:res}
\end{table}

>>>>

\begin{figure}[htb]
\begin{minipage}[b]{.48\linewidth}
  \centering
  \centerline{\includegraphics[width=4.0cm]{RGB_1}}
%  \vspace{1.5cm}
  \centerline{Sample from patient 498959}\medskip
\end{minipage}
\hfill
\begin{minipage}[b]{0.48\linewidth}
  \centering
  \centerline{\includegraphics[width=4.0cm]{GT_1}}
%  \vspace{1.5cm}
  \centerline{Associated ground truth}\medskip
\end{minipage}
%
%
%\begin{minipage}[b]{.48\linewidth}
 % \centering
%  \centerline{\includegraphics[width=4.0cm]{RGB_2}}
%  \vspace{1.5cm}
%  \centerline{Sample from patient 581910}\medskip
%\end{minipage}
%\hfill
%\begin{minipage}[b]{0.48\linewidth}
%  \centering
%  \centerline{\includegraphics[width=4.0cm]{GT_2}}
%  \vspace{1.5cm}
%  \centerline{Associated ground truth}\medskip
%\end{minipage}
%
%
\begin{minipage}[b]{.48\linewidth}
  \centering
  \centerline{\includegraphics[width=4.0cm]{RGB_3}}
%  \vspace{1.5cm}
  \centerline{Sample from patient 581910}\medskip
\end{minipage}
\hfill
\begin{minipage}[b]{0.48\linewidth}
  \centering
  \centerline{\includegraphics[width=4.0cm]{GT_3}}
%  \vspace{1.5cm}
  \centerline{Associated ground truth}\medskip
\end{minipage}
%
\caption{Random annotated samples from the dataset}
\label{fig:annotation}
%
\end{figure}

@@

%% Contribution as a dataset, small introduction
\noindent One of the contributions of this paper is the now publicly available 
nuclei detection dataset within HE stained histopathology images which 
can be found at \url{http://cbio.mines-paristech.fr/~pnaylor/BNS.zip}. This annotated dataset provides images clustered by 
patients. Each patient has at least 3 annotated $512 \times 512$ HE 
histopathology images with their associated ground truth. Each 
ground truth image is a $512 \times 512$ label image where each pixel value above 
$0$ is considered as the label of the corresponding nucleus. 
See figure \ref{fig:annotation} for an example of 
three annotated images. This annotation was conducted via the help of 
the software ITK-snap, \cite{py06nimg} \url{http://www.itksnap.org} by
the authors of this paper.

@@

%% Validation scheme
We have our training set $(A_l,B_l)_{l \in [1, N]}$ where N is equal to 
33, however each element $A_l$ belongs to a certain patients and 
several elements $A_l$ can belong to the same patient. As we are 
dealing with histopathology images, it is known that samples can widely 
vary from one patient to the other. We thus validate our model by a 
leave one patient out scheme. 
For this reason we use a leave-one-patient-out strategy: for a 
given set of hyper parameters, we 
train our model on every patient except one that is used for validation. 
Our final score is averaged over all patients.
Several metrics give a detailed assessment of the model quality: accuracy, intersection over union (IU),
F1 score and a performance score which is the mean between 
true positive rate and true negative rate.

@@

\section{Results and discussion}
\label{sec:result}
\noindent We conducted our experiments on GPUs via the caffe framework, 
\cite{jia2014caffe}. We present our results in table \ref{tab:res} where 
we averaged the metrics over all left out patients. We also added, for 
illustration purposes \ref{fig:prediction}, image predictions and 
associated 
probability maps to evaluate some differences between the classifiers. 
We notice that the simpler net, PangNet seems to have learnt simple 
rules such as color information. As soon as the nuclei are not
homogeneous and dark inside, the method fails ( "holes" in the
cells). On the 
contrary, deeper nets as FCN and DeconvNet have learnt deeper features 
and seem capable of recognizing whole cells. On these probability maps 
we applied our watershed segmentation and we can picture the results in 
the third 
column. By construction, our post-processing 
scheme is very sensitive to noise as we can see in the PangNet 
prediction, many unrelated minimas will lead to highly partitionned cell. 
This phenomenom also appears with the DeconvNet where undesired 
cuts were performed, like for the cell at the bottom left of the image. 
We picked $\lambda = 7$ which seemed to give a nice partitionning of 
the image, this value can be found by cross validation.
\begin{table}
\begin{tabular}{|c|c|c|c|c|}
\hline
  & PangNet & DeconvNet & FCN & Ensemble\\
 \hline
Accuracy  &       0.936 & 0.968 &0.958 & 0.968  \\
IU   &    0.759 &     0.856 & 0.857 & 0.861 \\
Recall     &       0.744  &     0.856 & 0.855 & 0.876\\
Precision   &       0.741 &     0.858 & 0.878 & 0.851\\
F1    &       0.742 &     0.856 & 0.866  & 0.863\\
% TP       &       0.744 &     0.856 & 0.855 & 0.876 \\
% TN      &       0.963 &     0.981 &  0.977 & 0.979\\
Performance    &       0.853 &     0.918 & 0.916 & 0.928\\
% Pixel error  &  0.063 &     0.032 & 0.042 & 0.032\\
\hline
\end{tabular}
\caption{Results}
\label{tab:res}
\end{table}
